Implications of Differential Evolution for Defect Prediction: Analytics Without Parameter Tuning Considered Harmful

### 2015-03-05 tuningpredictor.tex
Updates from ShareLaTeX

@@

\renewcommand{\baselinestretch}{0.8}
\scriptsize
\centering
  \begin{tabular}{r@{~}|r@{~}rr|r@{~}rr|r@{~}rr}
    & \multicolumn{3}{c|}{WHERE}&\multicolumn{3}{c|}{CART}& \multicolumn{3}{c}{Random Forest}\\\cline{2-10} 
    Goal & tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive&$\frac{\mathit{tuned}}{\mathit{naive}}$\\\hline
pd&242&13&19&7&1&9&13&1&10\\ 
prec&159&13&12&9&1&13&18&2&11\\
f&303&13&23&7&1&10&14&2&9 
  \end{tabular}
  \caption{For one train/test set pair (ANT),  time (in seconds) spent tuning,
  for different goals, or just running the ``off-the-shelf'' learner.}
\end{figure}

>>>>

XXX One consequence of this work is that it is possible to tune a detector such that it exhibits a wide range of performance scores. Given that, the next question becomes ``what performance scores do you want?''. This is an interesting issue since there is no single best answer. XXX

@@

\renewcommand{\baselinestretch}{0.8}
\scriptsize
\centering
  \begin{tabular}{r@{~}|r@{~}rr|r@{~}rr|r@{~}rr}
    & \multicolumn{3}{c|}{WHERE}&\multicolumn{3}{c|}{CART}& \multicolumn{3}{c}{Random Forest}\\\cline{2-10} 
    Goal & tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive&$\frac{\mathit{tuned}}{\mathit{naive}}$\\\hline
pd&71.4&1.2&60&4.4&0.1&44&7.1&0.2&36\\ 
prec&82.8&1.4&59&3.9&0.1&39&7.4&0.2&37\\
f&86.1&1.2&72&3.3&0.1&33&6.7&0.2&34
  \end{tabular}
  \caption{For one train/test set pair (ANT),  time (in seconds) spent tuning,
  for different goals, or just running the ``off-the-shelf'' learner.}
\end{figure}
